Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
Work in progress.

\begin{document}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\title{Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL}

\author{Q. Hong,
S. P. Platt,
A. V. Prokofiev,
E. Passoth
\thanks{further information}\\[2mm] 	% Your name
%\normalsize University of Central Lancashire \\ 							% Your institution
%\normalsize \href{qhong@uclan.ac.uk} 								% Your email address
\vspace{-5mm}
}

%----------------------------------------------------------------------------------------

\maketitle % Insert title
\todo{Check title, affiliations etc.}
%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
%	KEYWORDS
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\IEEEpeerreviewmaketitle

\section{Introduction}
\todo{Review introduction}
\IEEEPARstart{M}{onte} Carlo simulations of naked spallation neutron sources at Los Alamos Neutron Science Center (LANSCE) Weapons Neutron Research (WNR) Target 4\cite{Wender87} and the ANITA beam at the University of Uppsala The Svedberg Laboratory (TSL) have been completed using Geant4 and proved that Binary intranuclear cascade (INC) model gave a good representation of neutron spectra than Bertini INC model did\cite{Platt13}. Simulation result of neutron spectra using Geant4 with Binary INC model is below measurement data from ANITA neutron facility. It is likely to be influenced by our omission of collimator, shielding, and bending magnet component. This work is to verify this hypothesis is correct. In addition, we are intested in the gamma field at CUP and SUP in spallation neutron source at the ANITA neutron facility at TSL for SEE testing.
%------------------------------------------------

@@

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{SUP10ColSpatialDistribution10MeVRADECS.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at SUP}
    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Standard User Position.}
    \label{fig:SUPDensity}
\end{figure}

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{SUP10beamproFoldingRADECS.png}
% \todo{Show SUP profile, compared to measurements}
    \caption{Neutron profile at the Standard User Position}
    \label{fig:SUPProfile}
\end{figure}

@@

\begin{figure}[t]
    \vspace{2in}
%	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{SUPcomparedIFluxRADECS.eps}\hspace{\columnwidth}}\\
    \vspace{2in}
%	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{SUPNormalisedRADECS.eps}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:SUPSpectraComparison}
\end{figure}

@@

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{CUP10ColSpatialDistribution10MeV.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Close User Position.}
    \label{fig:CUPDensity}
\end{figure}

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{CUPTOF10beamproRADECS.png}
% \todo{Show CUP profile, compared to measurements}
    \caption{Neutron profile at the Close User Position}
    \label{fig:CUPProfile}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
%	SUP10ColSpatialDistributionAllG
        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionSUP}
    }\\
    \subfloat[CUP]{
%    CUP10ColSpatialDistributionAllG
        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionCUP}
    }
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

\begin{figure}
    \centering
    \vspace{2in}
    \hspace{\columnwidth}
    \includegraphics[width=3in]{gDYieldcomparedRADECS.eps}
    \caption{Calculated differential gamma spectra at CUP and SUP}
    \label{fig:DifferentialGammaSpectra}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergySUP}
    }\\
    \subfloat[CUP]{
        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergyCUP}
    }
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}

@@

\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

@@

%----------------------------------------------------------------------------------------

>>>>

\begin{document}

\title{
    Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL
}

\author{%
    Q. Hong,
    S. P. Platt,
    A. V. Prokofiev,
    E. Passoth
    \thanks{%
        Qian Hong and Simon Platt are with the University of Central Lancashire, England. Alexander Prokofiev and Elke Passoth are with the The Svedberg Laboratory, University of Uppsala, Sweden.
    }
}

\maketitle % Insert title
\todo{Check title, affiliations etc.}

@@

\section{Introduction}
\todo{Review introduction}
\IEEEPARstart{M}{onte} Carlo simulations of naked spallation neutron sources at Los Alamos Neutron Science Center (LANSCE) Weapons Neutron Research (WNR) Target 4\cite{Wender87} and the ANITA beam at the University of Uppsala The Svedberg Laboratory (TSL) have been completed using Geant4 and proved that Binary intranuclear cascade (INC) model gave a good representation of neutron spectra than Bertini INC model did\cite{Platt13}. Simulation result of neutron spectra using Geant4 with Binary INC model is below measurement data from ANITA neutron facility. It is likely to be influenced by our omission of collimator, shielding, and bending magnet component. This work is to verify this hypothesis is correct. In addition, we are intested in the gamma field at CUP and SUP in spallation neutron source at the ANITA neutron facility at TSL for SEE testing.

@@

\begin{figure}[t]
    \includegraphics[width=3in]{SUP10ColSpatialDistribution10MeVRADECS.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at SUP}
    \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the Standard User Position.}
    \label{fig:SUPDensity}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=3in]{SUP10beamproFoldingRADECS.png}
% \todo{Show SUP profile, compared to measurements}
    \caption{Neutron profile at the Standard User Position}
    \label{fig:SUPProfile}
\end{figure}

@@

\begin{figure}[t]
	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{ANITAIntYieldRADECS.eps}}\\
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{ANITALetYieldnormalisedRADECS.eps}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:SUPSpectraComparison}
\end{figure}

@@

\begin{figure}[t]
    \includegraphics[width=3in]{CUP10ColSpatialDistribution10MeV.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
    \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the Close User Position.}
    \label{fig:CUPDensity}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=3in]{CUPTOF10beamproRADECS.png}
% \todo{Show CUP profile, compared to measurements}
    \caption{Neutron profile at the Close User Position}
    \label{fig:CUPProfile}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \vspace{2in}
    \subfloat[SUP]{
%	SUP10ColSpatialDistributionAllG
        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionSUP}
    }\\
    \subfloat[CUP]{
%    CUP10ColSpatialDistributionAllG
        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionCUP}
    }
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=3in]{gDYieldcomparedRADECS.eps}
    \caption{Calculated differential gamma spectra at CUP and SUP}
    \label{fig:DifferentialGammaSpectra}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \vspace{2in}
    \subfloat[SUP]{
        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergySUP}
    }\\
    \subfloat[CUP]{
        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergyCUP}
    }
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}

@@

@@

\cleardoublepage
